\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2025-06-25 doc/paper-jss/sdmTMB-paper.Rnw
Don't include p-values for residuals

<<dog-residuals, fig.cap="Simulation-based randomized quantile residuals from the \\pkg{DHARMa} package. The statistical test is a two-sided Kolmogorov-Smirnov test of the null hypothesis that the residuals are drawn from a uniform(0, 1) distribution.", fig.asp=0.68, echo=TRUE, out.width="4in">>=
set.seed(42)
s <- simulate(fit, nsim = 500, type = "mle-mvn")
dharma_residuals(s, fit, test_uniformity = TRUE)
@

>>>>

<<dog-residuals, fig.cap="Simulation-based randomized quantile residuals from the \\pkg{DHARMa} package.", fig.asp=0.68, echo=TRUE, out.width="4in">>=
set.seed(42)
s <- simulate(fit, nsim = 500, type = "mle-mvn")
dharma_residuals(s, fit)
@
